### 2021-02-25 paper/fse21/abstract.tex
Fix typo in abstract

In this paper, we propose a novel technique to take advantage of the
high performance of dynamic analysis for JavaScript static analysis
in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
consists of three parts: 1) converting an abstract state to its corresponding
\textit{{\sealed} state}, 2) performing \textit{{\sealed} state}
on the {\sealed} state, and 3) converting a {\sealed} state
to its corresponding abstract state. By taking dynamic shortcuts
during static analysis, we can significantly improve the analysis
scalability and precision by using highly-optimized commercial JavaScript engines
and lessen the modeling efforts by performing {\sealed} execution for opaque code.
We formally define static analysis using dynamic shortcuts in the abstract
interpretation framework.  We actualize the technique via $\tool$, an
extended combination of SAFE and Jalangi, a static analyzer and a
dynamic analyzer, respectively.  We evaluated $\tool$ using
269 official tests of Lodash 4 library.
Our experiment shows that $\tool$ is \inred{6.30}$\x$ faster than the
baseline static analyzer, and it improves the precision to
\inred{reduce assertion fails by 12\% on average} by using {\sealed} execution for
\inred{12} opaque functions.
\end{abstract}

>>>>

In this paper, we propose a novel technique to take advantage of the
high performance of dynamic analysis for JavaScript static analysis
in a sound way by using \textit{dynamic shortcuts}.  A dynamic shortcut
consists of three parts: 1) converting an abstract state to its corresponding
\textit{{\sealed} state}, 2) performing \textit{{\sealed} execution}
on the {\sealed} state, and 3) converting a {\sealed} state
to its corresponding abstract state. By taking dynamic shortcuts
during static analysis, we can significantly improve the analysis
scalability and precision by using highly-optimized commercial JavaScript engines
and lessen the modeling efforts by performing {\sealed} execution for opaque code.
We formally define static analysis using dynamic shortcuts in the abstract
interpretation framework.  We actualize the technique via $\tool$, an
extended combination of SAFE and Jalangi, a static analyzer and a
dynamic analyzer, respectively.  We evaluated $\tool$ using
269 official tests of Lodash 4 library.
Our experiment shows that $\tool$ is \inred{6.30}$\x$ faster than the
baseline static analyzer, and it improves the precision to
\inred{reduce assertion fails by 12\% on average} by using {\sealed} execution for
\inred{12} opaque functions.
\end{abstract}
